Estimating duration in the presence of misclassification

### 2024-02-19 introduction.tex
ch5 proof

>>>>

HIGHLIGHT THE FLEXIBLE FRAMEWORK AS A CONTRIBUTION.
A framework for performing CIS-like simulations is available at \url{https://github.com/joshuablake/cisSimulation}.
A framework for fitting the class of models described here and in \cref{E-imperf-test} is available at \url{https://github.com/joshuablake/cisDurationModel}.
Code utilising these frameworks to perform the analysis described in this chapter is available at \url{https://github.com/joshuablake/cisRuns}.

### 2024-02-19 symbols.tex
ch5 proof

>>>>

From chapter 5
\begin{itemize}
    \item $b_i$ the day infection episode $i$ begins
    \item $\set{D}$ the set of test schedules with a detected infection episode
    \item $d_i$ the duration of infection episode $i$
    \item $e_i$ the day infection episode $i$ ends
    \item $f_A(t)$ the pdf of the duration estimate from chapter 4
    \item $f_C(t)$ the pdf of the duration estimate from Walker's analysis
    \item $k_t$ the belief in the ATACCC estimate at time $t$
    \item $h_t$ the estimate of the hazard at time $t$ according to ATACCC
    \item $p_{ia}$ the probability of an admissible infection episode occurring in an individual with test schedule $\sched_i$
    \item $p_{i\bar{a}}$ the probability of an inadmissible infection episode occurring in an individual with test schedule $\sched_i$
    \item $p_{iu}$ the probability of an undetected infection episode occurring in an individual with test schedule $\sched_i$
    \item $\Ncis$ the number of individuals in CIS
    \item $\ndet$ the number of detected infection episodes
    \item $n_{ia}$ the number of admissible infection episodes in individuals with test schedule $\sched_i$
    \item $n_{i\bar{a}}$ the number of inadmissible infection episodes in individuals with test schedule $\sched_i$
    \item $n_{iu}$ the number of undetectable infection episodes in individuals with test schedule $\sched_i$
    \item $n_\sched$ the number of unique test schedules in CIS
    \item $\ntot$ the total number of infection episodes
    \item $\nnodet$ the number of undetected infection episodes
    \item $\alpha_0$ the prior in the absence of ATACCC data
    \item $\alpha_i$ the admissible space for test schedule $i$
    \item $\beta_0$ the prior in the absence of ATACCC data
    \item $\beta_i$ the inadmissible space for test schedule $i$
    \item $\epsilon_t$ the random part of the RW2 model for $\lambda_{t+1}$
    \item $\eta_i$ the number of individuals with test schedule $i$
    \item $\theta$ the survival function parameters
    \item $\lambda_t$ the hazard at time $t$
    \item $\mu_{\epsilon_1}$ the mean of the prior on $\epsilon_1$
    \item $\mu_{\lambda_1}$ the mean of the prior on $\lambda_1$
    \item $\mu_\sigma$ the mean of the prior on $\sigma$
    \item $\sigma$ the standard deviation of the RW2 prior on $\lambda_t$
    \item $\sigma_{\epsilon_1}$ the standard deviation of the prior on $\epsilon_1$
    \item $\sigma_{\lambda_1}$ the standard deviation of the prior on $\lambda_1$
    \item $\tau_{\sched_i}(t)$ the time between $t$ and the next test for test schedule $i$
    \item $\Omega_i^C$ the undetected space for test schedule $i$
\end{itemize}
